How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
NM
worked on first draft of Sec 3

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately and efficiently solve the Stokes
  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
  boundary integral equation (BIE). Applying the same approach as our
  previous works~\citep{quaife2018boundary, chiu2020viscous}, we
  represent the velocity as the sum of a double-layer potential and a
  combination of Stokeslets and rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + \sum_{\ell=1}^{M}\left(
    S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
    \quad \xx \in \Omega,
  \label{eqn:velocity}
\end{align}
where 
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
  \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
  \eeta(\yy) \, ds_\yy.
  \label{eqn:velocityDLP}
\end{align}
Note that $\bd\Omega$ includes both the eroding bodies and the outer
boundary. The Stokeslet and the rotlets are
\begin{align}
  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(\log \rho_\ell +
  \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
  \quad
  R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
\end{align}
where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
$\cc_\ell$ is a point inside body $\ell$. If the density function,
Stokeslets, and rotlets satisfy the second-kind boundary integral
equation
\begin{subequations}
  \label{eqn:FredBIE}
  \begin{alignat}{3}
    \UU(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      \quad &&\xx \in \Gamma, \\
    \mathbf{0} &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      &&\xx \in \gamma_\ell, \: \ell = 1,\ldots,M, \\
    \llambda_\ell &= \int_{\gamma_\ell} \eeta(\yy) \, ds_\yy, 
      &&\ell = 1,\ldots,M, \\
    \xi_\ell &= \int_{\gamma_\ell} (\yy - \cc_\ell)^\perp \cdot 
      \eeta(\yy) \, ds_\yy, &&\ell = 1,\ldots,M,
  \end{alignat}
\end{subequations}
then the representation~\eqref{eqn:velocity} satisfies the Stokes
equations with the required boundary conditions~\eqref{eqn:StokesEq}. We
solve~\eqref{eqn:FredBIE} by discretizing $\gamma_\ell$ and $\Gamma$ at
equispaced collocation points, and then replacing the integrals with
quadrature rules. This results in a linear system with a
mesh-independent condition number, and it is solved iteratively with
GMRES.

Instead of evaluating the Stokes double-layer
potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we
convert the integral to a sum of contour integrals around Jordan curves
in $\CC$. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
similar notation for $\yy$, $\nn$, and $\eeta$. We also interpret
$\gamma$, the boundary of the $i^{th}$ grain or the bounding box
$\Gamma$, as a Jordan curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
\end{align}
We then define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
Then, the first and second components of the Stokes double-layer
potential are
\begin{subequations}
  \begin{align}
    u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
             \Re(v_3'(x)) + \Re(v_4(x)) \\
    u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
             \Im(v_3'(x)) + \Re(v_5(x)),
  \end{align}
  \label{eqn:velocityCauchy}
\end{subequations}
respectively. The hydrodynamic components of the deformation tensor are
\begin{subequations}
  \begin{align}
    \pderiv{u_1}{x_1} &= -\Re(v'_1(x)) + \Re(v''_3(x)) + \Re(v'_4(x))
                         -\Re(x)\Re(v''_1(x)) - \Im(x)\Re(v''_2(x)) \\
    \pderiv{u_1}{x_2} &= -\Re(v'_2(x)) - \Im(v''_3(x)) - \Im(v'_4(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_1} &= +\Im(v'_1(x)) - \Im(v''_3(x)) + \Re(v'_5(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_2} &= +\Im(v'_2(x)) - \Re(v''_3(x)) - \Im(v'_5(x))
                         +\Re(x)\Re(v''_1(x)) + \Im(x)\Re(v''_2(x)) 
  \end{align}
  \label{eqn:deformationCauchy}
\end{subequations}
Having the deformation tensor at hand, the vorticity can be shown to
satisfy
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
     \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
  \label{eqn:vorticityCauchy}
\end{align}
We note that the deformation tensor requires second-order derivatives of
Cauchy integrals, but the vorticity only requires first-order
derivatives.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature for Cauchy integrals}
The accuracy of our method is determined by the accuracy of the
quadrature rule applied to equation~\eqref{eqn:FredBIE}. Since we have
written the Stokes double-layer potential
velocity~\eqref{eqn:velocityCauchy}, deformation
tensor~\eqref{eqn:deformationCauchy}, and
vorticity~\eqref{eqn:vorticityCauchy} as a sum of Cauchy integrals and
their derivatives, the accuracy of the method depends on the accuracy of
computing a general Cauchy integral
\begin{align}
  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
  \label{eqn:cauchy1}
\end{align}
Here we describe a quadrature formulae that was first used to
approximate analytic functions~\cite{ioa-pap-per1991}, and then extended
to Stokes layer potentials~\cite{bar-wu-vee2015}. The quadrature
requires the boundary data of the analytic function~\eqref{eqn:cauchy1}
which satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
    \quad x_0 \in \gamma,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal value sense.
Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be determined
by its boundary data alone using the Cauchy Integral Theorem
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  \label{eqn:cauchyv}
  v(x) &= \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\gamma}
    \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\gamma}
    \frac{v^{-}(y)}{(y-x)^3} \, dy.
  \end{alignat}
\end{subequations}

To approximate the Cauchy integrals and its
derivatives~\eqref{eqn:cauchy}, the trapezoid rule achieves spectral
accuracy. For example, the Cauchy integral~\eqref{eqn:cauchyv} can be
approximated as
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^{N} 
    w_j \frac{v^{-}(y_j)}{y_j - x},
  \label{eqn:trap}
\end{align}
where $y_j$ are equispaced points on $\gamma$, $w_j = L/N$, and $L$ is
the length of $\gamma$. Because the integrand is both periodic and
smooth, given a fixed points $x$, the trapezoid rule achieves spectral
accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
error is not bounded uniformly with respect to $x$ because the
derivative of the integrand grows without bound as $x$ approaches
$\gamma$. This error is problematic for many of our simulations since we
allow for eroding bodies to be arbitrarily close to one another. In
contrast to the Cauchy integral~\eqref{eqn:cauchyv}, the integrand in
the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y) - v(x)}{y-x} \, dy = 0, \quad x \in \Omega,
  \label{eqn:trap2}
\end{align}
is bounded with respect to $x$, and therefore the error of the trapezoid
rule is bounded with respect to $x$. Applying the trapezoid rule, we
have
\begin{align}
  \frac{1}{2\pi i}\sum_{j=1}^{N} w_{j} 
    \frac{v^{-}(y_j) - v(x)}{y_j - x} \approx 0,
\end{align}
where the error is independent of $x$. Rearranging, we have
\begin{align}
  v(x) \approx \left(\frac{1}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}(y_j)}{y_j - x} w_j \right) \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
  \quad x \in \Omega.
  \label{eqn:vBary}
\end{align}
Note that the numerator in~\eqref{eqn:vBary} is identical to
equation~\eqref{eqn:trap}, while the denominator is an approximation of
the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the error
in the numerator and denominator grow, however, since the integrand in
equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
the ratio is bounded independent of $x$.

>>>>

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately and efficiently solve the Stokes
  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
  boundary integral equation (BIE). A BIE formulation has the advantage
  that all the unknowns are on the one-dimensional boundary of the
  domain. Therefore, only the boundary of the complex geometry must be
  discretized which we do with a spectrally accurate Fourier basis.
  Applying the same approach as our previous
  works~\citep{quaife2018boundary, chiu2020viscous}, we represent the
  velocity as the sum of a double-layer potential and a combination of
  Stokeslets and rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) + \sum_{\ell=1}^{M}\left(
    S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
    \quad \xx \in \Omega,
  \label{eqn:velocity}
\end{align}
where 
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
  \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
  \eeta(\yy) \, ds_\yy.
  \label{eqn:velocityDLP}
\end{align}
Note that $\bd\Omega$ includes both the eroding bodies and the outer
boundary. The Stokeslet and the rotlets are
\begin{align}
  S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(-\log \rho_\ell +
  \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
  \quad
  R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
\end{align}
respectively, where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell =
\|\rr_\ell\|$, and $\cc_\ell$ is a point inside body $\ell$. If the
density function, Stokeslets, and rotlets satisfy the second-kind
boundary integral equation
\begin{subequations}
  \label{eqn:FredBIE}
  \begin{alignat}{3}
    \UU(\xx) &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      \quad &&\xx \in \Gamma, \\
    \mathbf{0} &= -\frac{1}{2}\eeta(\xx) + \DDD[\eeta](\xx) + 
      \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) + R[\xi_\ell](\xx)\right), 
      &&\xx \in \gamma_\ell, \: \ell = 1,\ldots,M, \\
    \llambda_\ell &= \int_{\gamma_\ell} \eeta(\yy) \, ds_\yy, 
      &&\ell = 1,\ldots,M, \\
    \xi_\ell &= \int_{\gamma_\ell} (\yy - \cc_\ell)^\perp \cdot 
      \eeta(\yy) \, ds_\yy, &&\ell = 1,\ldots,M,
  \end{alignat}
\end{subequations}
then the representation~\eqref{eqn:velocity} satisfies the Stokes
equations with the required boundary conditions~\eqref{eqn:StokesEq}. We
solve~\eqref{eqn:FredBIE} by discretizing $\gamma_\ell$ and $\Gamma$ at
equispaced collocation points, and then replacing the integrals with
quadrature rules. This results in a linear system with a
mesh-independent condition number, and it is solved iteratively with
GMRES.

Instead of evaluating the Stokes double-layer
potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we
convert the integral to a sum of contour integrals around Jordan curves
in $\CC$. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_x$, and use
similar notation for $\yy$, $\nn$, and $\eeta$. We also interpret
$\gamma$, the boundary of the $i^{th}$ grain or the bounding box
$\Gamma$, as a Jordan curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
\end{align}
We then define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
Then, the first and second components of the Stokes double-layer
potential are
\begin{subequations}
  \begin{align}
    u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
             \Re(v_3'(x)) + \Re(v_4(x)) \\
    u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
             \Im(v_3'(x)) + \Re(v_5(x)),
  \end{align}
  \label{eqn:velocityCauchy}
\end{subequations}
respectively. The components of the deformation tensor are
\begin{subequations}
  \begin{align}
    \pderiv{u_1}{x_1} &= -\Re(v'_1(x)) + \Re(v''_3(x)) + \Re(v'_4(x))
                         -\Re(x)\Re(v''_1(x)) - \Im(x)\Re(v''_2(x)) \\
    \pderiv{u_1}{x_2} &= -\Re(v'_2(x)) - \Im(v''_3(x)) - \Im(v'_4(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_1} &= +\Im(v'_1(x)) - \Im(v''_3(x)) + \Re(v'_5(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_2} &= +\Im(v'_2(x)) - \Re(v''_3(x)) - \Im(v'_5(x))
                         +\Re(x)\Re(v''_1(x)) + \Im(x)\Re(v''_2(x)) 
  \end{align}
  \label{eqn:deformationCauchy}
\end{subequations}
Having the deformation tensor at hand, the vorticity can be shown to
satisfy
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
     \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
  \label{eqn:vorticityCauchy}
\end{align}
We note that the deformation tensor requires second-order derivatives of
Cauchy integrals, while the vorticity only requires first-order
derivatives.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature for Cauchy integrals}
The accuracy of our method is determined by the accuracy of the
quadrature rule applied to equation~\eqref{eqn:FredBIE}. Since we have
written the Stokes double-layer potential
velocity~\eqref{eqn:velocityCauchy}, deformation
tensor~\eqref{eqn:deformationCauchy}, and
vorticity~\eqref{eqn:vorticityCauchy} as a sum of Cauchy integrals and
their derivatives, the accuracy of the method depends on the accuracy of
computing a general Cauchy integral
\begin{align}
  v(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy.
  \label{eqn:cauchy1}
\end{align}
Here we describe a quadrature formulae that was first used to
approximate analytic functions~\cite{ioa-pap-per1991}, and then extended
to Stokes layer potentials~\cite{bar-wu-vee2015}. The quadrature method
requires the boundary data of the analytic function~\eqref{eqn:cauchy1}
which satisfies the Sokhotski-Plemelj jump relation
\begin{align}
  v^{-}(x_0) = \lim_{\substack{x \rightarrow x_0 \\ x \in \Omega}} \int_{\gamma}
    \frac{\eta(y)}{x-y}\, dy = -\frac{1}{2}\eta(x_0) - 
    \frac{1}{2\pi i} \int_{\gamma} \frac{\eta(y)}{x-y} \, dy,
    \quad x_0 \in \gamma,
    \label{eqn:SP}
\end{align}
where the last integral is interpreted in the principal value sense.
Here we are assuming that $\Omega$ is the bounded region interior to
$\gamma$. Once $v^{-}$ is calculated, $v(x)$ and its derivatives can be
determined by its boundary data alone using the Cauchy Integral Theorem
\begin{subequations}
  \label{eqn:cauchy}
  \begin{alignat}{3}
  \label{eqn:cauchyv}
  v(x) &= \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y)}{y-x} \,dy, \\
  v'(x) &= \frac{1}{2\pi i} \int_{\gamma}
    \frac{v^{-}(y)}{(y-x)^2} \, dy, \\
  v''(x) &= \frac{1}{\pi i} \int_{\gamma}
    \frac{v^{-}(y)}{(y-x)^3} \, dy.
  \end{alignat}
\end{subequations}

To approximate the Cauchy integrals and its
derivatives~\eqref{eqn:cauchy}, the trapezoid rule achieves spectral
accuracy. For example, the Cauchy integral~\eqref{eqn:cauchyv} can be
approximated as
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^{N} 
    w_j \frac{v^{-}(y_j)}{y_j - x},
  \label{eqn:trap}
\end{align}
where $y_j$ are equispaced points on $\gamma$, $w_j = L/N$, and $L$ is
the length of $\gamma$. Because the integrand is both periodic and
smooth, given a fixed point $x$, the trapezoid rule achieves spectral
accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
error is not bounded uniformly with respect to $x$ because the
derivative of the integrand grows without bound as $x$ approaches
$\gamma$. This error is problematic for many of our simulations since we
allow for eroding bodies to be arbitrarily close to one another, and we
often compute the velocity and vorticity at points in the fluid domain
that are close to an eroding body. In contrast to the integrand in the
Cauchy integral~\eqref{eqn:cauchyv}, the integrand in the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y) - v(x)}{y-x} \, dy = 0, \quad x \in \Omega,
  \label{eqn:trap2}
\end{align}
is bounded with respect to $x$, and therefore the error of the trapezoid
rule is bounded with respect to $x$. Applying the trapezoid rule, we
have
\begin{align}
  \frac{1}{2\pi i}\sum_{j=1}^{N} w_{j} 
    \frac{v^{-}(y_j) - v(x)}{y_j - x} \approx 0,
\end{align}
where the error is now uniformly bounded for all $x$. Rearranging, we
have
\begin{align}
  v(x) \approx \left(\frac{1}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}(y_j)}{y_j - x} w_j \right) \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
  \quad x \in \Omega.
  \label{eqn:vBary}
\end{align}
Note that the numerator in~\eqref{eqn:vBary} is identical to
equation~\eqref{eqn:trap}, while the denominator is an approximation of
the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the errors
in the numerator and denominator grow, however, since the integrand in
equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
the ratio is bounded independent of $x$.

The derivatives of the Cauchy integral in~\eqref{eqn:cauchy} can be
approximated with similar quadrature rules. For $x \in \Omega$, 
\begin{align}
  v'(x) &\approx \left(\frac{1}{2\pi i}\sum_{j=1}^{N}
    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j \right)
  \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^{N} \frac{1}{y_j-x} w_j\right), 
  \label{eqn:D1vBary} \\
  v''(x) &\approx \left(\frac{2}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j \right)
    \Bigg/
    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right),
  \label{eqn:D2vBary}
\end{align}
where the quadrature rule is spectrally accurate and the error is
independent of $x$. We note that
equations~\eqref{eqn:vBary},~\eqref{eqn:D1vBary},
and~\eqref{eqn:D2vBary} all assume that $x \in \Omega$, where $\Omega$
is the bounded region interior to the Jordan curve $\gamma$. However, in
our application, when $\gamma$ is one of the eroding bodies, $x$ is in
the exterior region of the Jordan curve. In this case, slightly
different identities are used, but they all guarantee that the trapezoid
rule achieves spectral accuracy with an error that is independent of
$x$. A complete description of the quadrature rules
for~\eqref{eqn:vBary} and~\eqref{eqn:D1vBary} are described by Barnett,
Wu, and Veerapaneni~\cite{bar-wu-vee2015}, and the quadrature rule
for~\eqref{eqn:D2vBary} is described in our previous
work~\cite{chiu2020viscous}.
